%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Python | OpenCV | NumPY | Scikit-Learn} % Job title
    {Machine Learning in robotics} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Predicts whether a certain batch of paddy grains is good, adulterated or ruined using several image processing techniques like object detection, contouring, image threshold and supervised machine learning models like support vector machines and logistic regression.}s
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Django | HTML | Cascading Style Sheets| JavaScript | Bootstrap | Git | MySQL} % Job title
    {Website : Compact} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a website that allows college professors to upload resources, assignments and attendance. All the students are notified of new activities and can keep track of projects, tests and deadlines.}
        \item {Used Django integrated with MySQL to maintain the back end of the project while the front end was developed using HTML, Cascading Style Sheets, JavaScript. Bootstrap was heavily involved in front end development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java | JavaFX} % Job title
    {Artificial Intelligent Checker Player} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a checkers game using JavaFX.}
        \item {Furthermore, the computer player uses min-max pruning algorithm to predict the opponents moves and responds accordingly.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python | Keras} % Job title
    {Emotion Recognition in Autistic Children using Convolution Neural Networks} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a deep convolution neural networks using Keras library to identify emotions in autistic children. The dataset of autistic children was acquired from Kaggle.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
